\documentclass[conference,compsoc,onecolumn]{IEEEtran}

\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{listings}
\usepackage{caption}
\usepackage{minted}
\usepackage[style=ieee, backend=biber, bibencoding=utf8, dashed=false]{biblatex}


\addbibresource{resources/bib/online.bib}

\title{Information Security for Web Services: Writing Assignment \#1}
\author{
  \IEEEauthorblockN{Christoph Stach}
  \IEEEauthorblockA{
    NTUST: National Taiwan University of Science and Technology\\
    Student ID: E10815023\\
    Email: christoph.stach@gmail.com
  }
}


\begin{document}
  \maketitle

  
  \section{Explain what is (system) interoperability?}

    System interoperability is the ability of ICT systems to communicate with each other \cite{whatisinteroperability}. 
    Today's IT infrastructure consists of many applications. 
    Often these applications (or systems) should be capable of interchanging pieces of information. This is leveraged by providing a service-oriented computing infrastructure. 
    Nowadays these infrastructures consist of many web services that can exchange data and information in different formats like \cite{json} or \cite{xml}.
    The data produced by web services can be consumed by many different applications (Dekstop applications, mobile phone applications, websites, and other web services).
    Modern web services are realized as REST-Services \cite{rest} or GraphQL \cite{graphql}-Services. Older ones are SOAP-Services \cite{soap} that are still existent in older IT infrastructures.
    Frameworks like  \cite{spring}, \cite{nestjs},\cite{apollo} and many more can help creating web service.
    
  \section{Why system interoperability is necessary for modern companies?}

    System interoperability is very important for modern companies. 
    Companies often have such a huge IT infrastructure that the exchange of information is necessary. 
    In today's world, a company without ICT Systems is not able to compete with other companies anymore \cite{whatisinteroperability}.
    Many things can be automated by ICT systems.
    To have a highly automated company system interoperability must be given. 
    As an example, the companies website needs to display the products the company is selling. Those are stored in an enterprise resource planning (ERP) system.
    The automate the process the website needs to able to fetch product details and prices from the ERP.
    Many companies analyze different things to predict the future most accurately and make profitable decisions.
    To analyze data from different ICT systems in a single place the systems need to provide interoperable interfaces like web services.

    
  \section{How do you achieve (system) interoperability prior to web services technology?}
  
    Today interoperability is achieved by ICT systems, providing web services. These have the benefit that they are loosely coupled and systems from different vendors can communicate with each other.
    It is even possible that web services are written in different programming languages, they can still work together. 
    Today's behavior we  call services-oriented were different ICT services provide web services that can communicate with each other.
    In the past, this technology didn't exist. ICT systems were object-oriented organized.
    Only ICT systems written in the same programming languages could communicate with each other and exchange information. 
    The reason for that is different programming languages use different data types which are not always completely compatible.
    Another solution to achieve interoperably was to grant other Systems direct access to the system's database, which is general a security issue \cite{databasesecurity}. 

    
  \printbibliography[heading=bibintoc]  
    
\end{document}
